### 2022-11-01 doc/src/VSLevel.tex
Add DPR to hvictl to specify default priority order of virtual interrupts
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

The format of \z{hvictl} is:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bit 30     & VTI \\
bits 27:16 & IID (\WARL) \\
bit 8      & IPRIOM \\
bits 7:0   & IPRIO \\
\end{displayLinesTable}
All other bits of \z{hvictl} are reserved and read as zeros.

@@

@@

\item
if \z{hvictl} fields VTI =~1 and $\mbox{IID} \neq \mbox{9}$:
\begin{tightList}
\item[+]
the major interrupt specified by \z{hvictl} fields IID and IPRIO.
\end{tightList}

@@

When no interrupt candidates satisfy the conditions of the list above,
\z{vstopi} is zero.
Else, \z{vstopi} fields IID and IPRIO are determined by the
highest-priority interrupt from among the candidates.
The usual priority order for supervisor level applies, as specified by
Table~\ref{tab:intrPrios-S} on page~\pageref{tab:intrPrios-S}, except
that priority numbers are taken from the candidate list above, not from
the supervisor-level \z{iprio} array.
As always, ties in nominal priority are broken by the default priority
order from Section~\ref{sec:majorIntrs}.
If bit IPRIOM (IPRIO Mode) of \z{hvictl} is zero,
IPRIO in \z{vstopi} is~1;
else, if the priority number for the highest-priority candidate is within the
range 1 to 255, IPRIO is that value;
else, IPRIO is set to either 0 or 255 in the manner documented
for \z{stopi} in Section~\ref{sec:stopi}.

>>>>

The format of \z{hvictl} is:\nopagebreak
\begin{displayLinesTable}[l@{\quad}l]
bit 30     & VTI \\
bits 27:16 & IID (\WARL) \\
bit 9      & DPR \\
bit 8      & IPRIOM \\
bits 7:0   & IPRIO \\
\end{displayLinesTable}
All other bits of \z{hvictl} are reserved and read as zeros.

@@

For a virtual interrupt specified for VS level by \z{hvictl},
if VTI =~1 and $\mbox{IID} \neq \mbox{9}$,
field DPR (Default Priority Rank) determines the interrupt's
presumed default priority order relative to a (virtual)
supervisor external interrupt (SEI), major identity~9, as follows:
\begin{displayLinesTable}
0 = interrupt has higher default priority than an SEI \\
1 = interrupt has lower default priority than an SEI \\
\end{displayLinesTable}
When \z{hvictl}.IID =~9, DPR is ignored.

@@

\item
if \z{hvictl} fields VTI =~1 and $\mbox{IID} \neq \mbox{9}$:
\begin{tightList}
\item[+]
the major interrupt specified by \z{hvictl} fields IID, DPR, and IPRIO.
\end{tightList}

@@

When no interrupt candidates satisfy the conditions of the list above,
\z{vstopi} is zero.
Else, \z{vstopi} fields IID and IPRIO are determined by the
highest-priority interrupt from among the candidates.
The usual priority order for supervisor level applies, as specified by
Table~\ref{tab:intrPrios-S} on page~\pageref{tab:intrPrios-S}, except
that priority numbers are taken from the candidate list above, not from
the supervisor-level \z{iprio} array.
Ties in nominal priority are broken as usual by
the default priority order from Section~\ref{sec:majorIntrs},
unless \z{hvictl} fields VTI =~1 and $\mbox{IID} \neq \mbox{9}$
(last item in the candidate list above), in which case
default priority order is determined solely by \z{hvictl}.DPR.
If bit IPRIOM (IPRIO Mode) of \z{hvictl} is zero,
IPRIO in \z{vstopi} is~1;
else, if the priority number for the highest-priority candidate is within the
range 1 to 255, IPRIO is that value;
else, IPRIO is set to either 0 or 255 in the manner documented
for \z{stopi} in Section~\ref{sec:stopi}.
